Master Thesis

### 2013-06-17 motivation.tex
This is the printed version.

The grammatical formalism of our choice for this task will be the
abstract categorial grammars (ACGs) \cite{de2001towards}. This framework
lets use lambda calculus to express the syntax-semantics interface in a
fashion similar to Montague's. Furthermore, elegant techniques for using
ACGs to implement DRT and SDRT using continuations have been
discovered (see \cite{de2006towards}, \cite{asher2011sdrt} and
\cite{asher2011montagovian}).

>>>>

The grammatical formalism of our choice for this task will be the
abstract categorial grammars (ACGs) \cite{de2001towards}. This framework
lets use lambda calculus to express the syntax-semantics interface in a
fashion similar to Montague's. Furthermore, elegant techniques for using
ACGs to implement DRT and SDRT using continuations have been discovered
(see \cite{de2006towards}, \cite{asher2011sdrt},
\cite{asher2011montagovian} and \cite{qian2011event}).
